LSST Alerts: Science-Driven Options for Packets and their Distribution

### 2020-01-10 dmtn-tbd.tex
statments re. stamp size

>>>>

\textcolor{red}{{\bf Could Postage Stamps Be Smaller? --}}
\citeds{LSE-163} describes the size of the postage stamp to be at least $6\arcsec \times 6\arcsec$ ($30\times30$ pixels), or large enough to encompass the entire footprint of the {\tt DIASource} (e.g., if trailed, extended). 
That is large enough to contain the angular diameter (30 kpc) of a Milky Way-like galaxy at a redshift of $z\approx0.5$, which will be a fairly typical supernova host galaxy in the LSST data set.
Since context is a science driver for producing stamps, it would not be desirable for them to be much smaller than $6\arcsec \times 6\arcsec$.
